{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-26 documents/experiment_1_data.tex
Ruler

\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c| } 
		\hline
		Exposure & kilocounts per 10s integration & Note \# \\
		\hline
		Autoclaved phage (0.2 mL) & 30 & \\ 
		Autoclaved p. (50 uL) & 32 & Run 8\\ 
		\hline
		Phage culture 'blank' & 8 & \\ 
		Water & 1 & \\
		\hline
		\multicolumn{3}{|c|}{\ntilde 10 or 20 us  } \\
		\hline
		 & \\ 
		\hline
		\multicolumn{3}{|c|}{Sweep from 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
		\hline
		\multicolumn{3}{|c|}{\ntilde 0.05 mm, \ntilde } \\
		\hline
		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, 0.2 uL/s, various pulse counts and termination} \\
		\hline 
		 Blank    & 8 & Li test 1\\
		 +           & 8 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 + \& shaper & 7 & Li test 1\\
 		 \hline
		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, various pulse counts and termination} \\
		\hline
		Sham & 5 & Smaller \\
		+ & 6 & Smaller \\ 
		+ & 6 & Smaller  \\ 
		\hline
		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, \ntilde 0.75 MV/m, 0.2 uL/s, basic buffer, but pH may not have been 10.6} \\
		\hline
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		Sham & 12 & Weakened  \\ 
		\hline
	\end{tabular}
\end{table}

Data from testing on bacteriophage. Data rounded (0.5 and above up) to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.

Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment.

Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples is not known. However, in no case did any tube approach the 22 to 30 kcounts of the autoclave.

@@

@@

In all cases, a thermal effect was implausible; the total energy in the pulse train precluded heating above the capsid melting temperature.\cite{Effects1951}

@@

However, as spectrometry was abandoned, this non-deterministic property caused significant issues while troubleshooting the fluorescence detection system, and \st{expedience} \st{\textit{laziness}} prompted us to disable this system, violating best practices.

@@

>>>>

\subsection{Data from testing on bacteriophage T4}
\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c| } 
		\hline
		Exposure & kilocounts per 10s integration & Note \# \\
		\hline
		Autoclaved phage (0.2 mL) & 30 & \\ 
		Autoclaved p. (50 uL) & 32 & Run 8\\ 
		\hline
		Phage culture 'blank' & 8 & \\ 
		Water & 1 & \\

		\hline
		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
		\hline
		Sham   & 12 & Run 8 t4,5...\\
		+ & 11 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		+  & 12 & Run 8 t4,5...\\
		\hline
		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, phage degraded with basic buffer} \\
		\hline
		Blank (0 min) & 14 & Run 9\\
		Blank (\ntilde 15 min) & 17 & Run 9\\
		Sham (\ntilde 15 min) & 5 & Run 9\\
		Blank (\ntilde 4 hr) & 24 & Run 9\\
		\hline
		+  & 14 & Run 11\\
		Sham & 17 & Run 11\\
		\hline
		\multicolumn{3}{|c|}{NF capillary, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
		\hline
		Sham & 12 & Run 12\\
		+    & 10 & Run 12\\
		\hline
		\multicolumn{3}{|c|}{0.2 mm channel, 6 to 12 GHz, average approximately 150 V/m, 10 or 20 us CW pulses} \\
		\hline
		 Sham & 12 & CPWG micro-\\
 		 +    & 10 & CPWG micro-\\
 		\hline

		\multicolumn{3}{|c|}{\ntilde 0.05 mm, \ntilde } \\
		\hline

		\multicolumn{3}{|c|}{\ntilde 0.2 mm channel, 0.2 uL/s, various pulse counts and termination} \\
		\hline 
		 Blank    & 8 & Li test 1\\
		 +           & 8 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 +           & 7 & Li test 1\\
 		 + \& shaper & 7 & Li test 1\\
 		 \hline

		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, various pulse counts and termination} \\
		\hline
		Sham & 5 & Smaller \\
		+ & 6 & Smaller \\ 
		+ & 6 & Smaller  \\ 
		\hline

		\multicolumn{3}{|c|}{\ntilde 0.05 mm channel, 0.2 uL/s, basic buffer, tainted as pH may not have been 10.6} \\
		\hline
		Sham & 12 & Weakened \\ 
		Blank & 11 & Weakened  \\ 
		Blank & 12 & Weakened  \\ 
		Blank & 9 & Weakened  \\ 
		+ & 11 & Weakened \\
		+ (no term) & 11 & Weakened \\ 
		+ & 9 & Weakened \\ 
		\hline
	\end{tabular}
\end{table}

As noted, this field reached a reasonable level of quality many decades ago, and many of the most troubling issues had already been encountered and addressed satisfactorily in experimental designs\cite{Biological1984}. In some cases, these are thoroughly characterized and described. UWB rat paper. But it seems to me that each worker (myself included!) is using their own test arrangement; and yet the studies are not so different as to require such customization. analysis anew to ascertain the very details of how the study was conducted, rather than simply its results.

By using yet another exposure cell, introducing an new set of unknown artifacts, we are actually hampering this field; and so we encourage anyone who may wish to replicate this result not to use this system, but one of the existing, well-characterized systems mentioned below or in the literature.

For in-vitro research, it seems to me that perhaps this field is running into the issues Feynman's rat-races \cite{Cargo}. There are a large number of very tricky variables.

 In this case, we were limited by budget - primarily the power amplifiers we have access to.

It occurs to me that perhaps a set of exquisitely characterized standardized test cells and procedures would be helpful; and a requirement that any papers on the topic either use such a cell, or if their study requires some exceptional treatment, to follow an established procedure to add a new cell to the standard.

 Data rounded to the nearest thousand photon counts per 10 seconds. %thoroughly characterized.

Background ('blank', in notes) readings measure the amount of DNA present in the phage culture tube before any treatment. 'sham' indicates

Repeatability between test conditions was not terrific. The source of the \ntilde 5000 count variation between some equivalent samples, and between "blank" and "sham", is not known. However, in no case did any sample\wikinote{verify} approach the 22 to 30 kcounts of the autoclave.

@@

The electrodes are only 1 oz copper thick (35 micrometers); but the engraved channel is significantly deeper. \cite{Nanosecond2006} and simulations seem to suggest that this is not a serious problem, but it is possible that the field in much of the channel was much lower than predicted.

@@

In all cases, a thermal effect was made implausible; the total energy in the pulse train precluded heating above the capsid melting temperature\cite{Effects1951}.

Only tubes 4 onwards are shown from Run 8 data because the capillary purging protocol was changed. In the final iteration, the autosampler was disconnected. The capillary was flushed with water; then the leuer lock was disconnected, air withdrawn into the syringe, and then purged through the capillary and fluidic channel.

@@

However, as spectrometry was abandoned, this non-deterministic property caused considerable issues while troubleshooting the fluorescence detection system, and \st{expedience} \footnote{laziness} prompted us to disable this system at run 9, defying best practices on blinded trials.

@@

\clearpage

### 2021-02-26 documents/lessons_learned.tex
Ruler

This was written in 4 parts: first, rough lab notes were made, then this was cleaned up into a long thesis-like document, and then this was compressed into the final paper. However, in that final compression step, a lot of "texture" and pedagogy was lost.

>>>>

This was written in 4 parts: first, rough lab notes were made, then this was cleaned up into a long thesis-like document, and then this was compressed into the final paper. However, in that final compression step, a lot of "texture" and pedagogy was lost on the first draft, when writing as terse as possible.

Don't worry about repeating yourself; duplicating sections in different contexts is fine.
